Market-based Mechanisms for Resource Scheduling

### 2013-12-18 paper/paper.tex
Adding fairness job completion graph and description

@@

Finally, Figure \ref{img:reg_fairness} displays the split-wise share of cluster resources each of the five frameworks are allocated in the market-based mechanism. Under high contention, all five frameworks have queued tasks to run, and we see that each framework gets roughly a fifth of the cluster resources. This indicates the market-based mechanism allocates resources fairly , similar to DRF.

>>>>

\includegraphics[width=0.5\textwidth]{images/relative_completion_times.png}
\caption{Relative average job completion times between DRF and auctions for all frameworks.}
\label{img:relative}
\end{figure}

@@

Finally, Figure \ref{img:relative} displays the relative average job completion time between DRF and the market-based mechanism for the five frameworks. As we see, the ratio is roughly 1.0 for all frameworks, which indicates the market-based mechanism is roughly as fair as DRF, and that jobs complete at the same approximate rate.
